Cycle Route Uptake and Scenario Estimation (CRUSE): an approach for developing strategic cycle network planning tools

### 2024-03-26 paper.tex

Routes in CRUSE are generated by CycleStreets, a not-for profit
transport consultancy and web development company who provide
application programming interfaces (APIs) supplying a range of datasets
for cycle planning and advocacy. Although based in Cambridge, UK,
CycleStreets provide routing services `by cyclists, for cyclists'
internationally, including in Ireland. The CycleStreets routing engine
is based on OpenStreetMap (OSM) data, which is continuously updated by a
global community of volunteers.

@@

We calculated three network types for each disaggregated (`jittered') OD
pair: `Fastest', `Balanced' and `Quietest'. As outlined on the
CycleStreets'
\href{https://www.cyclestreets.net/help/journey/howitworks/}{website},
the fastest routes minimize journey time, accounting for traffic lights
and surface type. The `Quietest' route type minimizes busy sections of
road, allowing high `diversion factors' from the fastest route on
quieter but less direct ways (often avoiding roads and interactions with
motor vehicles altogether where possible). The `Balanced' route type is
a compromize between the two, minimising journey time while avoiding the
busiest roads. Allowing users to switch between these three route types
enables them to consider the trade-offs between directness and `cycle
friendliness' when planning new infrastructure, as shown in
Figure~\ref{fig-route-types}.

These map are available on the `Route types' page for each county (see
\href{https://cruse.bike/kildare/route-types}{cruse.bike/kildare/route-types}).
In addition to showing the estimated routes under each scenario, the
page also presents summary statistics on the network:

>>>>

Routes in CRUSE are generated by CycleStreets, a not-for profit
transport consultancy and web development company who provide
application programming interfaces (APIs) supplying a range of datasets
for cycle planning and advocacy internationally, including in Ireland.
The CycleStreets routing engine is based on OpenStreetMap (OSM) data,
which is continuously updated by a global community of volunteers.

@@

The CycleStreets routing engine accounts for hilliness and traffic
signals, based on substantial experience generating cycle routes for
utility and leisure cyclists worldwide. The resulting routes are
designed to indicate the route choices of confident, moderately
confident, and less confident cyclists with three route options provided
for each OD pair as described below. It would be possible to use other
routing engines and custom profiles and cost functions in the future,
for example to simulate the impact of implementing traffic signals which
are optimised for cycling throughput, a feature not currently available
in CycleStreets that could be explored in future work.

We computed three route types for each disaggregated (`jittered') OD
pair: `Fastest', `Balanced' and `Quietest'. As outlined on the
CycleStreets'
\href{https://www.cyclestreets.net/help/journey/howitworks/}{website},
the fastest routes minimize journey time, accounting for traffic lights
and surface type. The `Quietest' route type minimizes busy sections of
road, allowing high `diversion factors' from the fastest route on
quieter but less direct ways (often avoiding roads and interactions with
motor vehicles altogether where possible). The `Balanced' route type is
a compromize between the two, minimising journey time while avoiding the
busiest roads. Allowing users to switch between these three route types
enables them to consider the trade-offs between directness and `cycle
friendliness' when planning new infrastructure, as shown in
Figure~\ref{fig-route-types}. These different network maps are available
on the `Route types' page for each county (see
\href{https://cruse.bike/kildare/route-types}{cruse.bike/kildare/route-types}
for Kildare, for example). In addition to showing the estimated routes
under each scenario, the page also presents summary statistics on the
network:
